Lost in the woods: shifting habitats can lead phylogeography astray

### 2025-05-19 manuscript/phylogeo.tex
added affiliation and data availability

\begin{document}
\title{Lost in the woods: shifting habitats can lead phylogeography astray}
\author{Richard A.~Neher}
\affiliation{Biozentrum, University of Basel and Swiss Institute of Bioinformatics, Switzerland \looseness=-5}
\email{richard.neher@unibas.ch}

@@

\section*{Materials and methods}
All simulations were performed in Python and the associated code is available in the github repository \href{https://github.com/neherlab/phylogeography}{github.com/neherlab/phylogeography}.

>>>>

\begin{document}
\title{Lost in the woods: shifting habitats can lead phylogeography astray}
\author{Richard A.~Neher}
\affiliation{Biozentrum, University of Basel and Swiss Institute of Bioinformatics, Spitalstrasse 41, 4053 Basel, Switzerland \looseness=-5}
\email{richard.neher@unibas.ch}

@@

\section*{Materials and methods}
All simulations were performed in Python and the associated code is available in the github repository \href{https://github.com/neherlab/phylogeography}{github.com/neherlab/phylogeography}.
\subsection*{Data availability}
The manuscript reports exclusively simulation results. Aggregate output of the simulations are available in the github repository \href{https://github.com/neherlab/phylogeography}{github.com/neherlab/phylogeography} archived at \href{https://doi.org/10.5281/zenodo.15462925}{10.5281/zenodo.15462925}.
